Synthesizing Symmetric Lenses

### 2018-07-04 papers/SymmetricLenses/main.tex
Finished proof of Theorem 2

  Since $P_{S_1} = P_{\Downarrow S_1}$ and $P_{S_1} = P_{\Downarrow S_1}$, then 
  \begin{align*}
  P_{S_1}(s) &= \sum_{i=1}^n p_i * P_{SQ_i}(s)\\
  P_{S_2}(s) &= \sum_{j=1}^m q_m * P_{TQ_j}(s)
  \end{align*}
  hence
  \begin{align*}
  P_{S_1 \; |_p \; S_2}(s) &= p * (P_{S_1}(s)) + (1-p) * (P_{S_2}(s))\\
  &= p \left(\sum_{i=1}^n p_i * P_{SQ_i}(s)\right) + (1-p)\left(\sum_{j=1}^m q_m * P_{TQ_j}(s)\right)\\
  &= p * P_{\Downarrow S_1}(s) + (1-p) * P_{\Downarrow S_2}(s)\\
  &= P_{(\Downarrow S_1) \; |_p \; (\Downarrow S_2)}(s)
  \end{align*}
  which is what we wanted to show. This completes the proof.
\end{enumerate}
\end{proof}
\end{document}

>>>>

  Since $P_{S_1} = P_{\Downarrow S_1}$ and $P_{S_1} = P_{\Downarrow S_1}$, then 
  \begin{align*}
  P_{S_1}(s) &= \sum_{i=1}^n p_i * P_{SQ_i}(s)\\
  P_{S_2}(s) &= \sum_{j=1}^m q_m * P_{TQ_j}(s)
  \end{align*}
  hence
  \begin{align*}
  P_{S_1 \; |_p \; S_2}(s) &= p * (P_{S_1}(s)) + (1-p) * (P_{S_2}(s))\\
  &= p \left(\sum_{i=1}^n p_i * P_{SQ_i}(s)\right) + (1-p)\left(\sum_{j=1}^m q_m * P_{TQ_j}(s)\right)\\
  &= p * P_{\Downarrow S_1}(s) + (1-p) * P_{\Downarrow S_2}(s)\\
  &= P_{(\Downarrow S_1) \; |_p \; (\Downarrow S_2)}(s)
  \end{align*}
  which is what we wanted to show. This completes the proof.
\end{enumerate}
\end{proof}
\begin{theorem*}
  \label{thm:correct_entropy}
  If $\Regex$ is unambiguous and contains no empty subcomponents,
  $\EntropyOf{\Regex}$ is the entropy of $\mathcal{L}(\Regex)$.
\end{theorem*}
\begin{proof}
Given a discrete set $X$ and a probability distribution $P$ on $X$, we define the entropy $H(X)$ of $X$ by
$$H(X) = -\sum_{x \in X}P(x)\log_2{P(x)}$$
We prove the theorem by induction on $S$.
\begin{enumerate}
\item
($S = s$)

Then $\mathbb{H}(s) = 0 = H(\mathcal{L}(s)) = H(\{s\})$
\item
$(S = S^{*p})$

Since $S^{*p}$ is unambiguous, then $S$ is also anambiguous, and for each $s \in \mathcal{L}(S^{*p})$, there exist unique $t_1, \ldots, t_n \in \mathcal{L}(S)$ such that $s = t^s_1 \cdot \ldots \cdot t^s_{n_s}$. By the induction hypothesis, $H(\mathcal{L}(S)) = \mathbb{H}(S)$, thus
\begin{align*}
H(\mathcal{L}(S^{*p})) &= - \sum_{s \in \mathcal{L}(S^{*p})} P_{S^{*p}}(s) \log_2 P_{S^{*p}}(s)\\
&= -(1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_n) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i)\log_2 \left(p^n * (1 - p) * \prod_{i=1}^n P_S(s_i)\right)\\
&= -(1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_n) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i)\left(n \log_2 p  + \log_2 (1 - p) + \log_2 \left(\prod_{i=1}^n P_S(s_i)\right)\right)\\
&= -(1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_n) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i)\left(n \log_2 p  + \log_2 (1 - p) + \log_2 \left(\prod_{i=1}^n P_S(s_i)\right)\right)\\
&= -(1-p) * \log_2 p \sum_n n * p^n \sum_{\substack{(s_1, \ldots, s_n) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i)
-(1-p) * \log_2 (1 - p) \sum_n p^n \sum_{\substack{(s_1, \ldots, s_n) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i) \\
&-(1-p)\sum_n p^n \sum_{\substack{(s_1, \ldots, s_n) \\ s_i \in \mathcal{L}(S)}} \prod_{i=1}^n P_S(s_i)\log_2 \left(\prod_{i=1}^n P_S(s_i)\right)\\
&= -\log_2 p * \frac{p}{(1-p)} -\log_2 (1 - p) 
-(1-p)\sum_n p^n H(\mathcal{L}(S^n))\\
&= -\log_2 p * \frac{p}{(1-p)} -\log_2 (1 - p) 
-(1-p)\sum_n p^n n H(\mathcal{L}(S))\\
&= -\log_2 p * \frac{p}{(1-p)} -\log_2 (1 - p) 
-\frac{p}{(1-p)} * H(\mathcal{L}(S))\\
&= \frac{p}{(1-p)}(H(\mathcal{L}(S)) - \log_2 p) -\log_2 (1 - p)\\
&= \frac{p}{(1-p)}(\mathbb{H}(S) - \log_2 p) -\log_2 (1 - p)
\end{align*}
\item
($S = S_1 \cdot S_2$)

Since $S$ is unambigous, then $S_1$ and $S_2$ are also unambiguous, and for each $s \in \mathcal{L}(S_1 \cdot S_2)$ there exists a unique $s_1 \in \mathcal{L}(S_1)$ and a unique $s_2 \in \mathcal{L}(S_2)$ such that $s = s_1 \cdot s_2$. By the induction hypothesis, $H(\mathcal{L}(S_1)) = \mathbb{H}(S_1)$ and $H(\mathcal{L}(S_2)) = \mathbb{H}(S_2)$, hence
\begin{align*}
H(\mathcal{L}(S_1 \cdot S_2))(s) &= -\sum_{s_1 \in S_1} \sum_{s_2 \in S_2}P_{S_1}(s_1)*P_{s_2}(s_2) \log_2(P_{S_1}(s_1)*P_{S_2}(s_2))\\
&= -\sum_{s_1 \in S_1} P_{S_1}(s_1)\sum_{s_2 \in S_2}P_{s_2}(s_2) (\log_2(P_{S_1}(s_1) + \log_2 P_{S_2}(s_2)))\\
&= -\sum_{s_1 \in S_1} P_{S_1}(s_1) \sum_{s_2 \in S_2}P_{S_2}(s_2)\log_2(P_{S_1}(s_1)) + \sum_{s_1 \in S_1} P_{S_1}(s_1)\sum_{s_2 \in S_2} P_{S_2}(s_2)\log_2 P_{S_2}(s_2)\\
&= -\sum_{s_1 \in S_1} P_{S_1}(s_1) \log_2(P_{S_1}(s_1)) + \sum_{s_2 \in S_2} P_{S_2}(s_2)\log_2 P_{S_2}(s_2)\\
&= H(\mathcal{L}(S_1)) + H(\mathcal{L}(S_2))\\
&= \mathbb{H}(S_1) + \mathbb{H}(S_2)
\end{align*}
\item
($S = S_1 \; |_p \; S_2$)

Since $S$ is unambiguous, then $S_1$ and $S_2$ are also unambiguous, and every $s \in \mathcal{L}(S_1 \; |_p \; S_2)$ is either in $\mathcal{L}(S_1)$ or in $\mathcal{L}(S_2)$. By the induction hypothesis, $H(\mathcal{L}(S_1)) = \mathbb{H}(S_1)$ and $H(\mathcal{L}(S_2)) = \mathbb{H}(S_2)$. Then
\begin{align*}
H(\mathcal{L}(S_1 \; |_p \; S_2)) &= -\sum_{s \in \mathcal{L}(S_1)}(p * P_{S_1}(s))\log_2 (p * P_{S_1}(s)) - \sum_{s \in \mathcal{L}(S_2)}((1-p) * P_{S_2}(s))\log_2 ((1-p) * P_{S_2}(s))\\
&=- p\sum_{s \in \mathcal{L}(S_1)}P_{S_1}(s)(\log_2 p + \log_2 P_{S_1}(s)) - (1-p)\sum_{s \in \mathcal{L}(S_2)}P_{S_2}(s)(\log_2 (1-p) + \log_2 P_{S_2}(s))\\
&= p * (\log_2 p +  H(\mathcal{L}(S_1))) + (1-p) * ( \log_2 (1-p) + H(\mathcal{L}(S_2)))\\
&= p * (\log_2 p +  \mathbb{H}(S_1)) + (1-p) * ( \log_2 (1-p) + \mathbb{H}(S_2))\\
\end{align*}
\end{enumerate}
\end{proof}
\end{document}
